On the discretization of Laplace's equation with Neumann boundary conditions on polygonal domains

### 2020-06-10 paper_lap/JCP_response2/04nprelim.tex
update

The Nystr\"{o}m method proceeds as follows. We begin by constructing a discretization of the boundary $\Gamma$ with nodes {\color{blue}$x_1,\dots,x_N,$} and weights $w_1,\dots,w_N,$ which enable interpolation of the left- and right-hand sides of the boundary integral equation
\begin{align}\label{eqn:numpreint}
f(s) = -\frac{\sigma(s)}{2} + \int_0^L k(t,s) \,\sigma(t)\, {\rm d} t
\end{align}
with precision $\epsilon.$ In other words, given {\color{blue}$f(x_i),-\sigma(x_i) + \int_0^L k(t,x_i) \,\sigma(t)\, {\rm d} t,$} for $i=1,\dots,N,$ the values $f(s)$ and $-\sigma(s)/2 + \int_0^L k(t,s) \,\sigma(t)\, {\rm d} t$ can be obtained for all $0 \le s \le L$ to within $\epsilon.$

@@

The boundary $\Gamma$ is separated into a collection of intervals which are at least a fixed distance $\delta$  (measured in terms of arclength) away from a corner and the collection of intervals of length $2 \delta$ centered about each corner. The former are discretized using a standard smooth quadrature rule such as nested Gauss-Legendre quadrature while the latter are discretized using a custom set of interpolation nodes constructed in the following way.

First, all functions of the form $x^\mu,$ $\mu \in \{0\} \cup [1/2,50],$ $x \in [0,1]$ are discretized using nested Gauss-Legendre panels in $x$ and a single Gauss-Legendre panel in $\mu$. This creates a $N \times M$ matrix where $N$ denotes the number of spatial discretization points $r_i$ and $M$ denotes the number of $\mu_j$ chosen. $M$ and $N$ are increased until it is guaranteed that using Lagrange interpolation from the nested discretization the function $x^\mu$ can be interpolated to within an $L^2$ error less than $\epsilon$ on the interval $[0,1]$ for any $\mu$ in the specified range. A singular value decomposition is then performed on the $N\times M$ matrix. Let $K$ denote the number of singular values greater than $\epsilon.$ The right singular vectors correspond to discretizations of an orthonormal set of functions $\phi_1,\dots,\phi_K$ such that $x^\mu$ is in the span of $\phi_1,\dots,\phi_K$ to within an accuracy of $\epsilon.$

Finally, a set of interpolation points $x_j,$ $j=1,\dots,K$ and quadrature weights $w_j,$ $j=1,\dots,K$ are chosen for $\phi_1,\dots,\phi_K$ such that the matrix $U_{ij} = \phi_i(x_j) \sqrt{w_j}$ is well-conditioned. In practice suitable interpolation points can be obtained by using the roots of $\phi_{K+1}$ and calculating the corresponding weights by solving a linear system. The corresponding discretization nodes and weights for the corner-containing intervals of $\Gamma$ are obtained by suitable translations and scalings of $\{x_j\}$ and $\{w_j\}.$

@@

Once the discretization has been constructed it is necessary to construct appropriate quadrature for the integrals appearing in equation (\ref{eqn_1std}). When \upd{$x_i$} and $t$ do not belong to the same corner panel (in particular when either is not itself contained in a corner panel) then the weights and nodes associated with the discretization can be used as the quadrature rule. When $s_i$ corresponds to a corner panel special care must be taken. Instead, using an algorithm for generating generalized Gaussian quadratures \cite{bremer2010}, quadrature nodes are chosen which integrate
\begin{align}
\int_{0}^\delta k(t,\upd{x_j}) \tilde{\phi}_j(t)\,{\rm d}t
\end{align} 
where $\tilde{\phi}_j$ is a suitably scaled and translated copy of the singular function obtained in the discretization step, and for ease of exposition we assume that the corner panel corresponds to $(-\delta,\delta)$ in the parametrization with $t=0$ corresponding to the corner itself. Moreover, in light of symmetry between the two legs of the wedge it suffices to design quadratures assuming  \upd{$x_j$} lies in the half of a corner panel parametrized by $(-\delta,0).$
\begin{remark1}
Due to scale invariance, it suffices to compute quadratures for 
\begin{align}
\int_{0}^1 k(t,-x_j) {\phi}_j(t)\,{\rm d}t,
\end{align} 
where $x_j$ was one of the original discretization nodes generated on the interval $[0,1].$
\end{remark1}
\begin{remark1}
By interpolating from the discretization nodes to these quadrature nodes we obtain a set of weights $\tilde{W}_{i,j}$ such that if \upd{$x_1,\dots,x_{2K}$} correspond to the discretization of a corner parametrized by $(-\delta,\delta)$ with $0$ corresponding to the corner then
\begin{align}
\left| \int_{-\delta}^\delta k(t,\upd{x_i}) \, \tilde{\phi}_m(t)\,{\rm d}t - \sum_{j=1}^{2K} \tilde{W}_{\upd{i,j}} \tilde{\phi}_{m}(\upd{x_j}) \right| < \epsilon
\end{align}
for all $i=1,\dots,2K$ and $m=1,\dots,K.$
\end{remark1}

After all the quadratures have been constructed the result is an $N \times N$ linear system the solution of which gives an approximation to $\sigma$ sampled at the discretization nodes.

@@

The results of this algorithm are summarized in the following theorem (see \cite{}).
\upd{
\begin{theorem}
Let $A$ the integral operator corresponding to the interior Dirichlet problem, i.e. 
\begin{equation}
A[\sigma](s) = -\frac{\sigma(s)}{2} + \int_{0}^{L} k(t,s) \sigma(t) dt \, . 
\end{equation}
Let $\uA \in \mathbb{R}^{N\times N}$ denote the corresponding discretized matrix. In particular if $f \in S_\epsilon $ is piecewise analytic and 
\begin{equation}
S[f] = (f(x_{1})\sqrt{w_{1}},f(x_{2})\sqrt{w_{2}},\ldots f(x_{N}) \sqrt{w_N} )^{T} = \underline{f} \, ,
\end{equation}
then
\begin{align}
\underline{\sigma} = \uA^{-1} {\uf}
\end{align}
can be interpolated to a function $\tilde{\sigma}$ which is within $\epsilon$ of the true density $\sigma$ in an $L^2$-sense. 
\end{theorem}
}

@@

>>>>

The Nystr\"{o}m method proceeds as follows. We begin by constructing a discretization of the boundary $\Gamma$ with nodes {\color{blue}$x_1,\dots,x_N,$} and weights $w_1,\dots,w_N,$ which enable interpolation of the left- and right-hand sides of the boundary integral equation
\begin{align}\label{eqn:numpreint}
f(s) = -\frac{\sigma(s)}{2} + \int_0^L k(t,s) \,\sigma(t)\, {\rm d} t
\end{align}
with precision $\epsilon.$ In other words, given {\color{blue}$f(x_i),$ and $-\sigma(x_i)/2 + \int_0^L k(t,x_i) \,\sigma(t)\, {\rm d} t,$} for $i=1,\dots,N,$ the values $f(s)$ and $-\sigma(s)/2 + \int_0^L k(t,s) \,\sigma(t)\, {\rm d} t$ can be obtained for all $0 \le s \le L$ to within $\epsilon.$

@@

The boundary {\color{olive}$\Gamma$ is divided into a collection of disjoint pieces each of which are at least a fixed distance $\delta$  (measured in terms of arclength) away from a corner, and a collection of pieces of length $2 \delta$ centered about each corner. }The former are discretized using a standard smooth quadrature rule such as {\color{red}nested} Gauss-Legendre quadrature while the latter are discretized using a custom set of interpolation nodes constructed in the following way.

First, all functions of the form $x^\mu,$ $\mu \in \{0\} \cup [1/2,50],$ $x \in [0,1]$ are discretized {\color{olive} in $x$ using an adaptive interpolation scheme based on Gauss-Legendre panels}, and {\color{olive}in $\mu$ using} a single Gauss-Legendre panel for the range $[1/2,50].$ This creates a $N_x \times (N_\mu+1)$ matrix where $N_x$ denotes the number of spatial discretization points $r_i$ and $N_\mu$ denotes the number of $\mu_j$ chosen. The extra row in the matrix corresponds to the special case when $\mu = 0.$ $N_x$ and $N_\mu$ are increased until it is guaranteed that using Lagrange interpolation from the nested discretization the function $x^\mu$ can be interpolated to within an $L^2$ error less than $\epsilon$ on the interval $[0,1]$ for any $\mu$ in the specified range. A singular value decomposition is then performed on the $N_x \times (N_\mu+1)$ matrix. Let $K$ denote the number of singular values greater than $\epsilon.$ The left singular vectors correspond to discretizations of an orthonormal set of functions $\phi_1,\dots,\phi_K$ such that $x^\mu$ is in the span of $\phi_1,\dots,\phi_K$ to within an accuracy of $\epsilon.$

Finally, a set of interpolation points $x_j,$ $j=1,\dots,K$ and quadrature weights $w_j,$ $j=1,\dots,K$ are chosen for $\phi_1,\dots,\phi_K$ such that the matrix $U_{ij} = \phi_i(x_j) \sqrt{w_j}$ is well-conditioned. In practice suitable interpolation points can be obtained by using the roots of $\phi_{K+1}$ and calculating the corresponding weights by solving a linear system. The corresponding discretization nodes and weights for the corner-containing intervals of $\Gamma$ are obtained by suitable translations and scalings of $\{x_j\}$ and $\{w_j\}.$ {\color{olive}We note that in practice, to achieve an accuracy of $10^{-15}$ for all powers $\mu \in \{0\} \cup [1/2,50],$ $x \in [0,1],$ only about $35$ nodes are required (i.e. $K = 35$).}

@@

Once the discretization has been constructed it is necessary to construct appropriate quadrature for the integrals appearing in equation (\ref{eqn_1std}). When \upd{$x_i$} and $t$ do not belong to the same corner panel (in particular when either is not itself contained in a corner panel) then the weights and nodes associated with the discretization can be used as the quadrature rule. When $s_i$ corresponds to a corner panel special care must be taken. Instead, using an algorithm for generating generalized Gaussian quadratures \cite{bremer2010}, quadrature nodes are chosen which integrate
\begin{align}
\int_{0}^\delta k(t,\upd{x_i}) \tilde{\phi}_j(t)\,{\rm d}t
\end{align} 
where $\tilde{\phi}_j$ is a suitably scaled and translated copy of the singular function obtained in the discretization step, and for ease of exposition we assume that the corner panel corresponds to $(-\delta,\delta)$ in the parametrization with $t=0$ corresponding to the corner itself. Moreover, in light of symmetry between the two legs of the wedge it suffices to design quadratures assuming  \upd{$x_j$} lies in the half of a corner panel parametrized by $(-\delta,0).$
\begin{remark1}
Due to scale invariance, it suffices to compute quadratures for 
\begin{align}
\int_{0}^1 k(t,-x_i) {\phi}_j(t)\,{\rm d}t,
\end{align} 
where $x_i$ was one of the original discretization nodes generated on the interval $[0,1].$
\end{remark1}
\begin{remark1}
By interpolating from the discretization nodes to these quadrature nodes we obtain a set of weights $\tilde{W}_{i,j}$ such that if \upd{$x_1,\dots,x_{2K}$} correspond to the discretization of a corner parametrized by $(-\delta,\delta)$ with $0$ corresponding to the corner then
\begin{align}
\left| \int_{-\delta}^\delta k(t,\upd{x_i}) \, \tilde{\phi}_m(t)\,{\rm d}t - \sum_{j=1}^{2K} \tilde{W}_{\upd{i,j}} \tilde{\phi}_{m}(\upd{x_j}) \right| < \epsilon
\end{align}
for all $i=1,\dots,2K$ and $m=1,\dots,K.$
\end{remark1}

After all the quadratures have been constructed the result is an $N \times N$ linear system the {\color{olive}scaled} solution of which gives an approximation to $\sigma$ sampled at the discretization nodes.

@@

The results of this algorithm are summarized in the following theorem (see \cite{hoskins2019numerical}).
\upd{
\begin{theorem}
Let $A$ the integral operator corresponding to the interior Dirichlet problem, i.e. 
\begin{equation}
A[\sigma](s) = -\frac{\sigma(s)}{2} + \int_{0}^{L} k(t,s) \sigma(t) dt \, . 
\end{equation}
Let $\uA \in \mathbb{R}^{N\times N}$ denote the corresponding discretized matrix. In particular if $f \in S_\epsilon $ is piecewise analytic and 
\begin{equation}
S[f] = (f(x_{1})\sqrt{w_{1}},f(x_{2})\sqrt{w_{2}},\ldots f(x_{N}) \sqrt{w_N} )^{T} = \underline{f} \, ,
\end{equation}
then, {\color{olive}after a suitable rescaling,}
\begin{align}
\underline{\sigma} = \uA^{-1} {\uf}
\end{align}
can be interpolated to a function $\tilde{\sigma}$ which is within $\epsilon$ of the true density $\sigma$ in an $L^2$-sense. 
\end{theorem}
}

@@

{\color{olive}For ease of exposition, here we describe the exterior Neumann problem though an identical procedure can be used for the interior Neumann problem. In the latter case it is well-known that the naive boundary integral equation formulation has a one-dimensional nullspace (corresponding to the fact that solutions to the corresponding PDE are unique only up to a constant). Using standard techniques (see \cite{} for example) this issue can be corrected and the method of this paper can be applied in a straightforward manner.}
